Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-06-11 paper/paper.Rmd
redo blocking intro

#### Spatial blocking (blockCV)

"Spatial Blocking" (\pkg{blockCV} package [@blockCV]) creates homogeneous blocks across the study area splitting observations into different zones [@bahn2012, @wenger2012].
Multiple "blocks" are then combined into a partition, following the number of folds specified by the user.
For example, in a five-fold scenario, the method would combine one fifth of all blocks into a partition (with five partitions in total).

The way how the blocks are created can be manifold: Supplying a numeric value in meters via argument `theRange` (named just `range` in {mlr3spatiotempcv}) will create a quadratic block pattern across the study area.
The aggregation of zones can either be random (default) (`selection = "random"`), systematic (`selection = "systematic"`) or checkerboard structure (`selection = "checkerboard"`).

@@

#### Spatial tiling (sperrorest)

@@

```{r tile, fig.cap="Spatial tiling with arguments `rows` and `cols`.", out.width="40%", fig.pos="ht"}
resampling_tiles = rsmp("spcv_tiles",
  nsplit = c(3L, 4L)
)

>>>>

"Spatial Blocking" creates homogeneous blocks across the study area splitting observations into different zones [@bahn2012, @wenger2012, @blockCV].
The creation of these zones can be diverse: one option is to supply rows and columns to subdivide the data into a grid.
Others make use of landscape patterns such as crop zones [@russ2010] or species presence [@blockCV] to determine an initial partitioning.

Implementations of blocking methods often provide additional options to fine tune these initial partitions, allowing for fine-grained partition creation.

\pkg{mlr3spatiotempcv} supports two "blocking" implementations: (1) "Spatial blocking" from package \pkg{blockCV} and (2) "Spatial Tiles" from \pkg{sperrorest}.

#### Spatial blocking --- blockCV

The "Spatial blocking" from package \pkg{blockCV} comes with various options to customize the zone creation.
Besides the choice of relying on an initial random  (default) (`selection = "random"`), systematic (`selection = "systematic"`) or checkerboard pattern (`selection = "checkerboard"`) for the final partition aggregation, support for SDM specific background data is built-in.
Supplying a numeric value in meters via argument `theRange` (named just `range` in {mlr3spatiotempcv}) will create a quadratic block pattern across the study area.
Ultimately, users can also supply a user-defined polygon which defines the zones.

After the initial block creation, multiple "blocks" are combined to form a partition, honoring the number of folds requested by the user.
For example, in a five-fold scenario with a grid of four columns and five rows, the method would combine one fifth of all blocks (= four blocks) into a single partition.

The following subsections showcase some of the introduced options.

@@

#### Spatial Tiles --- sperrorest

@@

```{r tile, fig.cap="Spatial tiling with arguments `rows` and `cols`.", out.width="40%", fig.pos="ht"}
resampling_tiles = rsmp("spcv_tiles", nsplit = c(3L, 4L))
